---
title: "TEST POST"
author: "Ben Smith"
date: "2017-09-23"
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_knit$set(root.dir = '/Users/benjaminsmith/GDrive/joint-modeling/reversal-learning/behavioral-analysis/reversallearning/')
```


```{r mygraph, echo=TRUE, message=FALSE, warning=FALSE}
getwd()
#source("nate_files/fitGroupsV3Onegroup.R")
#source("/Users/benjaminsmith/GDrive/joint-modeling/reversal-learning/behavioral-analysis/reversallearning/data_summarize.R")

library(ggplot2)
set.seed(42)
dat<-data.frame("x"=c(rnorm(1000,0,1)))

ggplot(dat, aes(x=x)) +
   geom_histogram(binwidth=0.1)
```


I am working on using a Bayesian model to estimate parameters for our reward learning data. I'm extending [Nate Haines' Double Update Model for Reversal Learning](https://rpubs.com/CCSL/hBayesDM) [@ahn2017revealing]. Nate modified the version available in his package hBayesDM to work with our dataset, which is a deterministic Reversal Learning task. I have since incrementally extended it to handle two different tasks (reward and punishment learning) and repeated runs.

$\beta + 1$

# References

